Data Processing: Disaster Declaration Summaries

### 2021-12-10 code/processing_code/processing-declarations.Rmd
Cleaning/Processing Update

* Raw data summarization and overview
* Removal of irrelevant variables
* Feature engineering to create duration of incident and response
* Summarization of key variables for each disaster declaration and state
* Saving the processed dataset as an .rds

>>>>

* Raw data summarization and overview
* Removal of irrelevant variables
* Feature engineering to create duration of incident and response as well as month and year of event
* Summarization of key variables for each disaster declaration and state
* Saving the processed dataset as an .rds
